Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-19 Tex/Old text/chapters/chapter02.tex
thesis updated text

\subsubsection{Controller Model}
Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}. However, in this study, in order to simplify, the term used is controller.

>>>>

\subsubsection{Controller Model}
\label{sec:controller}
Depending on the literature, the controller can receive different names: controller \cite{Hansen}, charge controller \cite{Mahanta} and \cite{Chauhan}, regulator \cite{Mellit}, DC-DC converter with MPPT and switch \cite{Dhanowa}, \cite{Yatimi}, \cite{Abdulateef}, \cite{Roy}. However, in this study, in order to simplify, the term used is controller.

### 2019-07-19 Tex/Old text/chapters/chapter03.tex
thesis updated text

The Fig. \ref{fig:systemverif3} shows the process to convert a real solar PV system to a model in order to be verified by a model checking.

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{systemverif4}
\centering
\caption{From real solar PV system verification to model checking. Source: adapted from \cite{Clarke2008}.}
\label{fig:systemverif3}
\end{figure}

The flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}.

@@

In \textbf{Step 1}, the PV input data %(e.g., load power demand and load energy consumption) 
and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}. In

\textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.

@@

%
%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above. For example, what does a failure mean? is it SAT?}
In a nutshell, the model checker will process the ANSI-C code with constraints ($C$) and properties ($P$) from the PV system, and the tool will automatically verify if the PV system requirements are met. If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design. However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.
%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
%
%
%---------------------------------------------------------------------
% \subsection{The case studies and the Algorithm}
%---------------------------------------------------------------------
%
% 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

@@

@@

Premise 1:

@@

@@

@@

After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$. With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.

@@

Nevertheless, if the verification engine does not fail, we can conclude that the PV system does not need further corrections up to the given bound $k$.
%
%\textcolor{red}{this sentence is unclear... After this process is started the battery autonomy verification, from line 31}. \textcolor{red}{this sentence is unclear... Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...  The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries. 
%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
%, and change their value every 1 h according with the algorithm created using the technique.
 \begin{algorithm}
 \caption{Model checking algorithm for stand-alone PV}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
  \STATE $sizing \_ check()$ \\
  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
  \STATE $SOC \leftarrow 100\%$ \\
%  \COMMENT {Starting with the PV generation time}
% \\ 
%\textit{LOOP Process}
 \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
	  \STATE $dischargeBattery \, in \, 1h()$ \\
%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
	  \STATE $assert (SOC \geq SOC \_ min)$ \\
%	  \STATE $battery \, autonomy \, verification()$ \\
  \ENDFOR
  \FOR {$startPVgeneration$ to $endPVgeneration$}
    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
    \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
    \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
    \COMMENT {If-then-else sequence to imitate charge controller work}
    \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
    \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
    \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
      \STATE stop battery charge \COMMENT {PV feed the house}
    \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
    \ENDIF
    \STATE $assert (SOC \geq SOC \_ min)$ \\
    \STATE $hour \leftarrow hour+1$ \\
   \ENDFOR
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

@@

In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section \textcolor{red}{XXX}. This variant was created during this Thesis.

@@

Examples of specification used by our method include house demand, energy, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models.

-----------

There are four particular differences related to the traditional CEGIS described in Figure XX:

@@

\subsection{Optimization Assumptions and Premises}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Fig.~\ref{fig:validation} illustrates how a stand-alone solar PV project can be validated, passing through the traditional techniques, as manual, simulation, testing, and including the proposed automatic verification that is detailed in this Section. Note that, in one hand, the input information is the same for all the techniques, with the difference that in automated validation it is possible to define the bound $k$ to restrict the space-design search. However, in the other hand, the outputs are not equal, as the design-space coverage and the information presented as result.

\begin{figure}[h]
\includegraphics[width=1.0\textwidth]{PVprojectvalidation}
\centering
\caption{Comparative of project validation methods}
\label{fig:validation}
\end{figure}

Starting at his point, it will be showed how is done the automated verification.

The process begins with the conversion of the real PV system into a model. The Fig. \ref{fig:systemverif4} shows the process to convert a real solar PV system to a model in order to be verified by a model checking.

This illustration is a adaption from the general process of real system conversion depicted in Fig.~\ref{fig:systemverif}, detailing the inputs, outputs, and requirements of a real solar PV system.

Worth to mention that the model checking process is the same independently of the system that is validated, and the important is to chose a accurate model, to define the requirements/constraints, and to get correct information from the system components, in order to get sound and effective validation,

\begin{figure}[h]
\includegraphics[width=0.8\textwidth]{systemverif4}
\centering
\caption{From real solar PV system verification to model checking. Source: adapted from \cite{Clarke2008}.}
\label{fig:systemverif4}
\end{figure}

Moreover, the proposed flowchart of the automated verification method is illustrated in Fig.~\ref{fig:flowchartgeneral}. Those three steps are the high level description of how the automated verification, applied to solar PV systems, works.

@@

In \textbf{Step 1}, the PV input data %(e.g., load power demand and load energy consumption) 
and the formulae to check the sizing project, the mathematical model, the limits of the weather non-deterministic variables, are all written as an ANSI-C code~\cite{ANSI2018}.

\textbf{Assumption:} All the PV system model, user requirements, assumptions, and technical information from the PV system equipment is written as an ANSI-C code.

In \textbf{Step 2}, the sizing check of the PV system takes place: it will indicate if there is an error of sizing before to perform the automated verification of the system. This stage ensures that the system meets the standard project steps related to critical period method of sizing~\cite{Pinho}.

\textbf{Assumption:} before the automated verification, who performs the verification of the intended system behavior, is performed the sizing checking of the system. Moreover, if there is some error, the process stops, showing where is the sizing error.

\textbf{Assumption:} Sizing check is performed using critical period criteria.

@@

%
%\textcolor{red}{In the following paragraph you should related the output of our verification engine with the description of the BMC SAT or UNSAR given above. For example, what does a failure mean? is it SAT?}
In a nutshell, the model checker will process the ANSI-C code with constraints ($C$) and properties ($P$) from the PV system, and the tool will automatically verify if the PV system requirements are met. If it returns a failure (i.e., SAT), then the tool provides a counterexample, i.e., a sequence of states that leads to the property violation; this information can be used as a feedback to improve the PV system design. However, if the verification succeeds (i.e., UNSAT), there is no failure up to the bound $k$; therefore, the PV system will present its intended behavior up to the bound $k$.

\textbf{Assumption:} Use of bound $k$ to restrict the design-space and improve performance.

%, i.e., our verification engine does not give any guarantee that there is no error in bound $k+1$ unless some induction method is employed~\cite{DBLP:journals/sttt/GadelhaIC17}.
%
%
%---------------------------------------------------------------------
% \subsection{The case studies and the Algorithm}
%---------------------------------------------------------------------
%
% 
%and as backup at night 
%
%The 700 W system: 3 x 325 W PV panels connected in series, controller of 150 V/35 A with a DC-bus of 24 V, 4 x 220 Ah batteries (2 in series and 2 in parallel arrangement), and inverter of 700 W. 
%
%And the 1,200 W PV system: 4 x 325 W connected in series PV panels, with controller of 150 V/35 A  in a DC-bus of 48 V, 4 batteries of 120 Ah connected in series, and a 1,200 W inverter.
%
%As demonstrated at this work, the performance of the system is highly dependent of solar irradiance and temperature, that are specific of the deployed local (latitude and longitude).

@@

\textbf{Assumption:} day is divided in two parts (when there is and there is not PV generation, based in historical data from the location). Considering average temperature and solar irradiance (for every hour of the day) and the annual solar insolation (per day).

@@

\textbf{Premise:} The availability of temperature, solar irradiance, and solar insolation data from the location where the solar PV system will be used.

@@

\textbf{Premise:} Availability of data sheet from every element of the solar PV system to be validated.

\textbf{Premise:} It is necessary the detailed sized project of the PV system in order to perform the validation (list of equipment and configuration, as voltage, current and how they are connected).

\textbf{Assumption:} Load curve from every house must be estimated or measured. Moreover, the time step is of 1 hour, and it is not considered seasonality, i.e., the load curve is the same for the entire year.

@@

\textbf{Assumption:} Batteries are considered charged at the beginning of the project validation.

@@

After that, the model from PV generator is used in the function call of line 17, to produce the voltage and current considering the states of $G$ and $T$. With respect to every hour considered, the conditional \textit{if-elseif-endif} statements from lines 18, 20, 22, 24 and 26, will imitate the charge controller work as depicted in Table~\ref{table:controller} of Section~\ref{sec:controller}, performing the charge or discharge of batteries according to the value of different variables: if there is PV generation, the updated state of charge from batteries, the house's load and the set-up information of the PV system.

@@

Nevertheless, if the verification engine does not fail, we can conclude that the PV system does not need further corrections up to the given bound $k$.
%
%\textcolor{red}{this sentence is unclear... After this process is started the battery autonomy verification, from line 31}. \textcolor{red}{this sentence is unclear... Based on the fact that won't be PV generation after a given time of the day, the algorithm will only discharge the batteries until a new charging process (at the next day) to start.} \textcolor{red}{what do you mean by The formal verification is guaranteed?...  The formal verification is guaranteed by  macro to specific variables of the model, according lines 27 and 35.}
% and the non-deterministic variables $G$ and $T$ are considered during the formal verification of the system, otherwise, during the other two periods, there is no PV generation and just the power consumption from the backup batteries. 
%Within this 8h-period, $G$ and $T$ are automated verified with different values every one hour.
%, and change their value every 1 h according with the algorithm created using the technique.
 \begin{algorithm}
 \caption{Model checking algorithm for validation of stand-alone PV systems}
 \begin{algorithmic}[1]
 \begin{scriptsize}
 \renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
  \STATE $declare \, min \, and \, max \, solar \, irradiation[24h], \, and \, temperature[24h]$\\
  \STATE $declare \, case \, studies \, details: \, sizing \, and \, manufacturers \, data $ \\
  \STATE $sizing \_ check()$ \\
  \STATE $startPVgeneration \leftarrow findStartPVgeneration()$ \\
  \STATE $endPVgeneration \leftarrow findEndPVgeneration()$ \\
  \STATE $SOC \leftarrow 100\%$ \\
%  \COMMENT {Starting with the PV generation time}
% \\ 
%\textit{LOOP Process}
 \FOR {$1st \, 24h \, loop$ to $Nth \, 24h \, loop$}
  \FOR {$endPVgeneration+1$ to $startPVgeneration-1$}
	  \STATE $dischargeBattery \, in \, 1h()$ \\
%	  \STATE $autonomyCount \leftarrow autonomyCount+1$ \\
	  \STATE $assert (SOC \geq SOC \_ min)$ \\
%	  \STATE $battery \, autonomy \, verification()$ \\
  \ENDFOR
  \FOR {$startPVgeneration$ to $endPVgeneration$}
    \STATE $G \leftarrow nondet \_ uint(\,)$ \COMMENT {$G$ is non-deterministic variable}
    \STATE $T \leftarrow nondet \_ uint(\,)$ \COMMENT {$T$ is non-deterministic variable}
    \STATE assume ($Gmin \leq G \leq Gmax$) \COMMENT {restricting $G$ values}
    \STATE assume ($Tmin \leq T \leq Tmax$) \COMMENT {restricting $T$ values}
    \STATE $Imax, Vmax \leftarrow PVgenerationMODEL (G,T)$ \\
    \COMMENT {If-then-else sequence to imitate charge controller work}
    \IF {($battery \, is \, empty$) AND ($PV \, is \, generating$)}
      \STATE $chargeBattery \, in \, 1h()$ \COMMENT {PV feed the house}
    \ELSIF {($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
      \STATE FAIL with assert macro \COMMENT {Battery is empty and there is not PV generation}
    \ELSIF {NOT($battery \, is \, empty$) AND ($PV \, is \, generating$)}
      \STATE stop battery charge \COMMENT {PV feed the house}
    \ELSIF {NOT($battery \, is \, empty$) AND NOT($PV \, is \, generating$)}
      \STATE $dischargeBattery \, in \, 1h()$ \COMMENT {Battery feed the house}
    \ENDIF
    \STATE $assert (SOC \geq SOC \_ min)$ \\
    \STATE $hour \leftarrow hour+1$ \\
   \ENDFOR
  \ENDFOR
 \RETURN $(\,)$ 
  \end{scriptsize}
 \end{algorithmic} 
 \label{alg:verification-algorithm}
 \end{algorithm}

@@

Fig.~\ref{fig:optimization} illustrates how to obtain the optimal sizing of a stand-alone solar PV system, passing through the traditional techniques (manual, and simulation), and including the proposed automatic synthesis that is detailed in this Section.

One more time, as depicted in automated verification process, the input information is the same for all the methods, with the difference that in automated validation it is possible to define the bound $k$ to restrict the design-space search. And the outputs are not equal, as the design-space coverage and the, mainly, the final resulting.

\begin{figure}[h]
\includegraphics[width=1.0\textwidth]{optimalsizingprocess}
\centering
\caption{Comparative of optimal sizing methods}
\label{fig:optimization}
\end{figure}

@@

In Figure~\ref{CEGISalt}, it is pictured a variant of CEGIS previously presented in Section ~\ref{sec:ProgramSynthesis}, Fig.~\ref{Counter-Example-Guided-Inductive-Synthesis}. This variant was created during this Thesis and it will be detailed in this Section.

@@

Examples of specification used by the proposed method include solar insolation (site dependent), house power demand, house consumption energy, estimated load curve, AC voltage, and battery autonomy; we also provide a list of equipment specification and price from different manufacturers and models. Design assumptions are considered project specification as well. The assumptions regarding the optimal sizing are listed in Section~\ref{sec:OptAssumptions}.

There are four particular differences related to the traditional CEGIS described in Figure ~\ref{Counter-Example-Guided-Inductive-Synthesis} when compared to the variant CEGIS used in the proposed approach:

@@

\subsection{Optimization Assumptions and Premises}
\label{sec:OptAssumptions}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
